%        File: notes.tex
%     Created: Thu Sep 24 12:00 PM 2020 M
% Last Change: Thu Sep 24 12:00 PM 2020 M
%
\documentclass[a4paper]{article}

\usepackage{amsfonts}

\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}

\newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}}

\usepackage{amsmath}

\begin{document}

\section{Cauchy's Theorem}

\subsection{Contour Integrals}

\subsubsection{Definitions}
\begin{definition}[Integral of a curve in $\C$]
  \[
    \int^b_a h(t) dt = \int^b_a u(t) dt + i \int^b_a v(t) dt
  \]
  Where \(h: [a, b] \subset \R \to \C \)


\end{definition}


\begin{definition}[continuous curve or contour in $\C$]
  A continuous map \(\gamma : [a, b] \to \C\).
\end{definition}

\begin{definition}[piecewise $C^1$ curve]
  A curve whose interval $[a, b]$ we can divide up $a = a_0 < a_1 <  \ldots < a_n = b$ such that the derivative $\gamma'(t)$ exists on each open subinterval $(a_i, a_{a + 1})$ and is continuous on $[a_i, a_{i + 1}]$, where continuous on $[a_i, a_{i + 1}]$ means $\lim_{t \to a_i^+} \gamma'(t)$ and $\lim_{t \to a_{i+1^-}} \gamma'(t)$ exist.
\end{definition}

\begin{definition}[Integral of $f$ along $\gamma$]
  \[
    \int_\gamma f = \int_\gamma f(z) dz = \sum^{n - 1}_{i = o} \int^{a+1}_{a_i} f(\gamma(t))\gamma'(t) dt
  \]
  Where $f$ is a continuous and defined on an open set $A \subset \C$ and that $\gamma: [a, b] \to \C$ is a piecewise smooth curve satisfying $\gamma([a, b]) \subset A$.\\

  \paragraph{Relation to line integrals in a vector field}
  The definition is analogous to the following definition of a line integral from vector calculus. Let $P(x, y)$ and $Q(x, y)$ be  real-valued functions from $x$ to $y$ and let $\gamma$ be a curve.
  \[
    \int_\gamma P(x, y) dx + Q(x, y) dy = \sum^{n- 1}_{i = 0} \int^{a_{i+1}}_{a_i} [P(x(t), y(t)) \frac{dx}{dt} + Q(x(t), y(t)) \frac{dy}{dt}] dt
  \]
  where $\gamma(t) = (x(t), y(t))$.
\end{definition}

\begin{theorem}[Integral of $f$ along $\gamma$ in terms of $u$ and $v$]
  \[
  \int_\gamma f = \int_\gamma [u(x, y) dx - v(x, y)dy] + i \int_\gamma [u(x, y)dy + v(x, y)dx]
  \]
  \paragraph{How to remember}
  \[f(z) dz = (u + iv)(dx + i dy) = u dx - v dy + i(v dx + u dy)\]

\end{theorem}

\begin{definition}[Opposite curve $-\gamma$]
  \[
    - \gamma : [a , b] \to \C
  \]
  \paragraph{Relation to $\gamma$}
  $(- \gamma)(t) = \gamma(a + b - t)$.

  \paragraph{Geometric Intuition}
  $- \gamma $ is $- \gamma$ traversed in the opposite sense. 
\end{definition}

\begin{definition}[join or sum or union of $\gamma_1 + \gamma_2$ ]
  Suppose that $\gamma_1 : [a, b] \to \C$ and that $\gamma_2: [b, c] \to \C$ with $\gamma_1(b) = \gamma_2(b)$. 
  Define $\gamma_1 + \gamma_2 : [a, c] \to \C$ as 
  \[ (\gamma_1 + \gamma_2)(t) = \begin{cases} 
      \gamma_1(t) & \text{ if } t \in [a, b] \\ 
      \gamma_2(t) & \text{ if } t \in [b, c] \\ 
   \end{cases}
\]

  Where $\gamma_1$ and $\gamma_2$ are two curves. 
\end{definition}



\begin{theorem}[Integration properties of curves]
  \[
    \int_\gamma (c_1 f + c_2 g) = c_1 \int_\gamma f + c_2 \int_\gamma g
  \]

  \[
    \int_{-\gamma} f = - \int_\gamma f
  \]

  \[
    \int_{\gamma_1 + \gamma_2} f = \int_{\gamma_1} f + \int_{\gamma_2} f 
  \]

  Where $f, g$ are continuous functions, $c_1, c_2$ are complex constants, and $\gamma, \gamma_1, \gamma_2$ piecewise $C^1$ curves. 
\end{theorem}


\begin{definition}[Reparametrization]
  Let $\gamma : [a, b] \to \C$ be a piecewise smooth curve.
  A  piecewise smooth curve $\bar{\gamma}: [\bar{a}, \bar{b}] \to \C$ is called a reparametrization of $\gamma$ if there is some $C^1$ function $\alpha: [a, b] \to [\bar{a}, \bar{b}]$ with $\alpha'(a) = \bar{a}$ and $\alpha(b) = \bar{b}$ such that $\gamma(t) = \hat{\gamma}(\alpha(t))$
  \paragraph{Additional conditions}
  If $\gamma'(t) > 0 $ (hence increasing), $\gamma(a) = \bar{a}$, and $\alpha(b) = \bar{b}$ imply that $\bar{\gamma}$
  traverses the curve in the same sense that $\gamma$ does. This is sufficient and necessary to represent the same geometric curve.

  \paragraph{Non-differentiable points are maintained}
  The points in $[\bar{a}, \bar{b}]$ at which $\bar{\gamma}'$ does not exist correspond under $\alpha$ to the points of $[a, b]$ at which $\gamma'$ does not exist.
\end{definition}

\begin{theorem}[The Integral of $f$ is maintained over reparameterizations]
  If $\bar{\gamma}$  is a reparametrization  of $\gamma$, then 
  \[
    \int_\gamma f = \int_{\bar{\gamma}} f
  \]
  for any continuous $f$ defined on an open set contining the image of $\gamma = $ image of $\bar{\gamma}$.
\end{theorem}

\begin{definition}[Arc length of a curve ]
  \(\gamma : [a, b] \to \C\)
  \[
    l(\gamma) = \int_a^b|\gamma'(t)| dt = \int^b_a \sqrt{x'(t)^2 + y'(t)^2}dt
  \]

  \paragraph{Arc length is independent of parameterization}
  Geometrically similar to reparameterization. 

\end{definition}


\begin{definition}[Curve equalities and inequalities]
  Let $f$ be continuous on an open set $A$ and let $\gamma$ be a piecewise $C^1$ curve in $A$. If there is some constant $M \geq 0$ such that $|f(z)| \leq M$ for all points $z$ on $\gamma$ (that is, for all $z$ of the form $\gamma(t)$ for some $t$), then
  \[
    |\int_\gamma f| \leq M l(\gamma)
  \]

  \[
    |\int_\gamma f| \leq \int_\gamma |f| |dz|
  \]

  Where
  \[
    \int_\gamma |f| |dz| = \int_a^b |f(\gamma(t))|| \gamma'(t)| dt
  \]
\end{definition}
\paragraph{Usage}
Use this a s a basic tool to estimate the size of integrals. 


\begin{theorem}[Fundamental Theorem of Calculus - Contour Integrals]
  Suppose that $\gamma : [0, 1] \to \C$ is a piecewise smooth curve and that $F$ is a function defined and analytic on an open set $G$ containing $\gamma$. Assume $F'$ is continuous (later we find this is redundant). Then 
  \[
    \int_\gamma F'(z) dz = F(\gamma(1)) - F(\gamma(0)).
  \]
  In particular, if $\gamma(0) - \gamma(1)$, then 
  \[
    \int F'(z)dz = 0.
  \]
\end{theorem}

\begin{theorem}[Connection between zero derivative and constant]
If $f$ is a function defined and analytic on an open connected set $G \subset \C$, and if $f'(z) = 0$ for every point $z$ in $G$, then $f$ is constant on $G$. 
\end{theorem}


\begin{theorem}[Path Independence Theorem]
  Suppose $f$ is a continuous function on an open connected set $G \subset \C$.
  Then the following are equivalent: 
  \begin{itemize}
    \item Integrals are path-independent: If $z_0$ and $z_1$ are any two points in $G$ and $\gamma_0$ and $\gamma_1$ are paths in $G$ from $z_0$ to $z_1$, then 
      \[
        \int_{\gamma_0} f(z) dz = \int_{\gamma_2} f(z) dz.
      \]
    \item Integrals around closed curves are 0: If $\Gamma$ is a closed curve (loop) laying in $G$, then $\int_\Gamma f(z) dz = 0$.
    \item There is a (global) antiderivatve for $f$ on $G$: there is a function $F$ defined and analytic on all of $G$ such that $F'(z) = f(z)$ for all $z$ in $G$. 
  \end{itemize}
\end{theorem}

\begin{definition}[Conservative]
  A force field is called conservative if the net work done along a closed path is always $0$ or equivalently if the work done between two points is independent of the path taken between those points. 
\end{definition}

\begin{definition}[Potential Energy]
  If the force field is conservative, then the integral defines the potential energy, whose gradient is the original force field. 
\end{definition}

\subsection{Cauchy's Theorem - A First Look}
\begin{definition}[a simple closed curve]
  A curve is simple if it intersects itself only at its endpoints. 
\end{definition}

\begin{theorem}[Green's Theorem]
  For continuously differentiable functions \(P(x, y)\) and \(Q(x, y)\), 
  \[
    \int_\gamma P(x, y) dx + Q(x, y) dy = \int \int_A [\frac{\partial Q}{\partial x}(x, y) - \frac{\partial P}{\partial y}(x, y)] dx dy
    \]
  \paragraph{Used for}
    \begin{itemize}
      \item Making precise notions like the inside of curves clear. 
    \end{itemize}
\end{theorem}

\begin{theorem}[Preliminary Version of Cauchy's Theorem]
  Suppose that \(f\) is analytic, with derivative \(f\) continuous on and inside a simple closed curve \(\gamma\). 
  Then
  \[
    \int_\gamma f = 0
    \]
\end{theorem}

\begin{theorem}[Preliminary Version of the Deformation Theorem]
  Let \(f\) be analytic on a region \(A\) and let \(\gamma\) be a simple closed curve in \(A\). 
  Suppose that \(\gamma\) can be continuously deformed to another simple closed curve \(\bar{}\gamma\) without passing outside of the region \(A\) Then
  \[
    \int_\gamma f = \int_{\bar{\gamma}} f.
  \]
  \paragraph{Used for}
    \begin{itemize}
      \item To study curves over functions with a singularity inside of the curves.
       We can deform the curve to one that might be easier to evaluate. 
    \end{itemize}
\end{theorem}

\begin{definition}[Simply Connected]
  A region \(A \subset \C\) is called simply connected if \(A\) is connect and every closed curve \(\gamma\) in \(A\) can be deformed in \(A\) to some constant curve \(\bar{\gamma(t)} = z_0 \in A\). 
  
  \paragraph{}{Geometrically}
  \begin{itemize}
    \item A region without holes. 
  \end{itemize}

\end{definition}

\begin{definition}[Homotopic to a point or contractable to a point]
  Curves inside of a simply connect set. 

  \paragraph{}{Geometrically}
  \begin{itemize}
    \item A curve that does loop around a hole cannot be shrunk down to a point in \(A\) without leaving \(A\). This curve is not homotopic to a point. 
  \end{itemize}
\end{definition}


\begin{theorem}[Cauchy's Theorem for a Simply Connected Region]
  If \(f\) is analytic on a simply connected region \(G\) and \(\gamma\) is a closed curved in \(G\), then 
  \[
    \int_\gamma f = 0.
    \]
\end{theorem}

\begin{theorem}[Path Independence on Simply Connected Regions]
  Suppose that \(f\) is analytic on a simply connected region \(A\). 
  Then for any two curves \(\gamma_1\) and \(\gamma_2\) joining two points \(z_0\) and \(z_1\) in A, we have
  \[ \int_{\gamma_1} = \int_{\gamma_2} f\]
\end{theorem}

\begin{theorem}[Antiderviative Theorem]
  Let \(f\) be a function defined on a simply connected region \(A\). 
  Then there is an analytic function \(F\) defined on \(A\) that is unique up to an additive constant, such that \(F'(Z)  = f(z)\) for all \(z\) in \(A\). 
  We call \(F\) the antiderivative of \(f\) on \(A\). 
\end{theorem}


\begin{theorem}[Existence of Logarithms]
  Let \(A\) be a simply connected region and assume that \(0 \not \in A\).
  Then there is an analytic function \(F(z)\), unique up to the addition of multiples of \(2 \pi i\), such that \(e^{F(z)} = z\).
\end{theorem}

\begin{definition}[Branch of the Logarithm function on \(A\)]
  Our choice of a \(F\) such that \(e^{F(z)} = z\).
\end{definition}


\subsection{A Closer Look at Cauchy's Theorem}

\begin{theorem}[Cauchy's Theorem for a Rectangle]
  Suppose that \(R\) is a rectangular path with sides parallel to the axes and that \(f\)  is a function defined and analytic on an open an open set \(G\) containing \(R\) and its interior.
  Then 
  \[\int_R f = 0.\]

\end{theorem}

\begin{theorem}[Cauchy's Theorem for a Disk]
  Suppose that \(f : D \to \C\) is analytic on a disk \(D = D(z_0; \rho) \subset \C\).
  Then
  \begin{enumerate}
    \item \(f\) has an antiderivative on \(D\); that is there is a function \(F : D \to C\) that is analytic on \(D\) and that satisfies \(F'(z) = f(z)\) for all \(z\) in \(D\).
    \item If \(\Gamma\) is any closed curve in \(D\), then \(\int_\Gamma f = 0\).
  \end{enumerate}

\end{theorem}

\begin{theorem}[Cauchy's Theorem for Deleted Neighborhoods]
  Suppose that \(R\) is a rectangular path with sides parallel to the axes, that \(f\)is a function defined on an open set  \(G\) containing \(R\) and its interior, and that \(f\) is analytic on \(G\) except at some fixed point \(z_1\) in \(G\) which is not on the path \(R\). 
  Suppose that at \(z_1\), the function \(f\) satisfies \(\lim_{z \to z_1} (z - z_1) f(z) = 0 \). 
  Then \(\int_R f = 0\).

  \paragraph{Note}
  The limit condition holds under any of the following conditions.
  \begin{itemize}
    \item If \(f\) is bounded in a deleted neighborhood of \(z_1\)
    \item If \(f\) is continuous on  \(G\)
    \item If \(\lim_{z \to z_1} f(z)\) exists. 
  \end{itemize}
\end{theorem}

\begin{theorem}
  Suppose that \(R\) is a rectangular path with sides parallel to the axes, that \(f\) is a function defined and continuous on an open set \(G\) containing \(R\) and its interior, and that \(f\) is analytic on \(G\) except at some fixed point \(z_1\) in \(G\). 
  Then \(\int_R f = 0\).
\end{theorem}






\begin{theorem}[Strengthened Cauchy's Theorem for a Disk]
  Suppose that \(f : D \to \C\) is continuous on \(D\) and analytic on \(D \setminus \{z_1\}\) for some fixed \(z_1\) in \(D\). 
  Then
  \begin{enumerate}
    \item \(f\) has an antiderivative on \(D\); that is there is a function \(F : D \to C\) that is analytic on \(D\) and that satisfies \(F'(z) = f(z)\) for all \(z\) in \(D\).
    \item If \(\Gamma\) is any closed curve in \(D\), then \(\int_\Gamma f = 0\).
  \end{enumerate}
\end{theorem}


\begin{definition}[homotopic with fixed endpoints to \(\gamma_1\)]
  Suppose \(\gamma_0 : [0, 1] \to G \) and \(\gamma_1 : [0, 1] \to G \) are two continuous curves from \(z_0\) to \(z_1\) in a set \(G\). 
  We say that \(\gamma_0\) is homotopic with fixed endpoints to \(\gamma_1\) in \(G\) if there is a continuous function \(H : [0, 1] \times [0, 1] \to G\) from the unit square \([0, 1] \times [0, 1]\) into \(G\) such that 
  \begin{enumerate}
    \item \(H(0, t) = \gamma_0(t)\)  for \(0 \leq t \leq 1\). 
    \item \(H(1, t) = \gamma_1(t)\)  for \(0 \leq t \leq 1\). 
    \item \(H(s, 0) = z_0\) for \(0 \leq s \leq 1\). 
    \item \(H(s, 1) = z_1\)  for \(0 \leq s \leq 1\). 
  \end{enumerate}

  \paragraph{Note}
  If we fix \(\gamma_s(t) = H(s, t)\), then each \(\gamma_s\) is a continuous curve in \(G\). 

  \paragraph{Construction}
  One possible homotopy from one curve to the other is \(H(s, t) = t + t^{1 + s} i\).
   Another is \(H(s, t) = s(t + t^2 i) + (1 - s)(t + ti)\), which is the straight line between \(t + ti\) and \(t + t^2 i\)
\end{definition}

\begin{definition}[homotopic as closed curves in \(G\)]
  Suppose \(\gamma_0 : [0, 1] \to G \) and \(\gamma_1 : [0, 1] \to G \) are two continuous curves closed curves in a set \(G\). 
  We say that \(\gamma_0\) and \(\gamma_1\) are homotopic as closed curves in \(G\) if there is a continuous function \(h : [0, 1] \times [0, 1] \to G\) from the unit square \([0, 1] \times [0, 1]\) into \(G\) such that
  \begin{enumerate}
    \item \(H(0, t) = \gamma_0(t)\) for \(0 \leq t \leq 1\).
    \item \(H(1, t) = \gamma_1(t)\) for \(0 \leq t \leq 1\).
    \item \(H(s, 0) = H(s, 1)\) for \(0 \leq s \leq 1\).
  \end{enumerate}
  \paragraph{Note}
  If we fix \(\gamma_s(t) = H(s, t)\), then each \(\gamma_s\) is a continuous curve in \(G\). 

  \paragraph{Examples}
  The unit circle and ellipse are homotopic closed curves in an annulus. With one such \(H\) as \(H(s, t) = (1 + s) \cos t + i \sin t\). 
  If we would have used a disk instead of an annulus then both curves would have been homotopic to a point. Really an curve is homotopic to a point in a disk. 

  \paragraph{Usage}
  With more complicated regions, we often rely on our geometric intuition to determine when two curves are homotopic. 
  That is we try to decide whether we can continuously deform one curve to the other without leaving our region. 
  One reason is that we rarely use the homotopies \(H\) explicitly in practice; they are usually theoretical tools whose existence allows us to claim something else, such as equality of two integrals.
  In many situations homotopies might be quite complicated to write down.
  However, we must be prepared to justify our geometric intuition either with an explicit \(H\) or a proof of its existence in any particular situation. 


\end{definition}

\begin{definition}[Simply Connected]
  A connected set \(G\) is called simply connected if every closed curve \(\gamma\) in \(G\) is homotopic (as a closed curve) to a point in \(G\), that is, to some constant curve. 
\end{definition}


\begin{definition}[Convex Set]
  A set \(A\) is called convex if it contains the straight-line segment between every pair of its points. 
  That is, if \(z_0\) and \(z_1\) are in \(A\), then so is \(s z_1 + (s - 1) z_0\) for every number \(s\) between \(0\) and \(0\).
\end{definition}

\begin{theorem}
  If \(A\) is a convex region, then any two closed curves in \(A\) are homotopic as closed curves in \(A\), and any two curves with the same endpoints are homotopic with fixed endpoints. 
\end{theorem}

\begin{theorem}[A convex region is simply connected].
\end{theorem}

\begin{theorem}[Deformation Theorem]
  Suppose that \(f\) is an analytic function on an open set \(G\) and that \(\gamma_0\) and \(\gamma_1\) are piecewise \(C^1\) curves in \(G\). 
  \begin{enumerate}
    \item If \(\gamma_0 \) and \(\gamma_1\) are paths from \(z_0\) to \(z_1\) and are homotopic in \(G\) with fixed endpoints, then 
      \[\int_{\gamma_0} f = \int_{\gamma_1} f.\]
    \item If \(\gamma_0\) and \(\gamma_1\) are closed curves with are homotopic as closed curves in \(G\), then 
      \[\int_{\gamma_0} f = \int_{\gamma_1} f.\]
  \end{enumerate}

  \paragraph{Note}
  Technically the proof given in the book requires the homotopies to be smooth, but there is a proof without this restriction. 
\end{theorem}

\begin{definition}[Smooth homotopy]
  A homotopy \(H : [0, 1] \times [0, 1] \to G\) is called smooth if the intermediate curves \(\gamma_s(t)\) are piecewise \(C^1\) functions of \(t\) for each \(s\) and the cross curves \(\lambda_t(s)\) are piecewise \(C^1\) functions of \(s\) for each \(t\). 
\end{definition}

\begin{theorem}[Homotopy Form of Cauchy's Theorem]
  Let \(f\) be analytic on a region \(G\). 
  Let \(\gamma\) be a closed curve in \(G\) which is homotopic to a point in \(G\). Then
  \[\int_\gamma f = 0.\]
  
\end{theorem}






\end{document}



